Summer 2024 Report

### 2024-11-26 Relations/Report.tex
Updates to implication table

@@

\item{WN and UN and RP $\implies$ wfSeq - (~ R)}
\item {CR $\implies$ WCR}
\item {NF $implies$ UN}
\item {SN and WCR $\implies$ UN and WN}
\item {Ind and Inc $\implies$ SN} \sacomment{I don't think we have
a proof of this, should we include it, include it with a note that we're taking [TeReSe]'s word on it?}
\item {WCR, WN, and, Inc $\implies$ SN}
\item {WCR, WN, and RP $\implies$}
\item {CR and NF $\implies$ UN}
\item {CR $^{\leq1} \implies$ CR}

@@

Table listing highest "confluence" property implied
by the conjunction of row and column.
\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
  \toprule
  CP & CR & WCR & WNFP & WUN \\
  \midrule
  SN  & & & & \\
  WN  & & & & \\
  WN*  & & & & \\
  BP $\land$ CP   & & & & \\
  BP  & & & & \\
  CP  & & & & \\
  \bottomrule
\end{tabular}

Table listing highest "normalization" property implied 
by the conjunction of row and column.
\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
  \toprule
  CP & CR & WCR & WNFP & WUN \\
  \midrule
  SN  & & & & \\
  WN  & & & & \\
  WN*  & & & & \\
  BP $\land$ CP   & & & & \\
  BP  & & & & \\
  CP  & & & & \\
  \bottomrule
\end{tabular}

>>>>

\begin{dfn}
  A relation $R$ has the \emph{weak normal form property} (WNFP) if
 $a \tto b$ and $a \tto c$  $\implies$
 $c \tto b$, for all $a,c \in A$ and all normal form $b \in A$.
\end{dfn}

@@

\texttt{i+ : WN R $\to$ UN$\to$ R $\to$ bounded R}

\item{WN and UN and RP $\implies$ wfSeq - ($\sim$ R)}

\texttt{ii3- :  WN R $\to$ UN R $\to$ RP R $\to$ isWFseq- ($\sim$R R)}

\item {CR $\implies$ WCR}

\texttt{CR$\to$WCR : CR R $\to$ WCR R }

\item {NF $implies$ UN}
\sacomment{Need to prove}

\item {SN and WCR $\implies$ UN and WN}
\sacomment{Need to proove}
\texttt{}

\item {Ind and Inc $\implies$ SN} \sacomment{I don't think we have
a proof of this, should we include it, include it with a note that we're taking [TeReSe]'s word on it?}

\item {WCR, WN, and, Inc $\implies$ SN}

\item {WCR, WN, and RP $\implies$ SN}

\item {CR $\implies$ NF $\implies$ UN}

\texttt{i-4 : confluent R $\to$ NFP R $\to$ UN R}

\item {CR $^{\leq1} \implies$ CR}

@@

Table listing highest "confluence" property implied
by the conjunction of row and column.

\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
  \toprule
  & CP & CR & WCR & WNFP & WUN  \\
  \midrule
  SN  & ? & CR & CR & (Should be CR?)  & ?  \\
  WN  & ? & CR & (Not CR) & ? & ? \\
  WN* & ? & CR & ? & ? & ? \\
  BP $\land$ CP & ? & CR & ? & ? & ? \\
  BP  & ? & CR & ? & ? & ? \\ 
  CP  & ? & CR & ? & ? & ? \\
  \bottomrule
\end{tabular}

Table listing highest "normalization" property implied 
by the conjunction of row and column.

\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
  \toprule
  & CP & CR & WCR & WNFP & WUN \\
  \midrule
  SN  &?& SN & SN & SN & SN \\
  WN  &?& (Not SN) & (Not SN) & ? & ? \\
  WN*  &?& ? & ? & ? & ? \\
  BP $\land$ CP   &?& ? & ? & ? & ? \\
  BP  &?& ? & ? & ? & ? \\
  CP  &?& (not CP or BP) & ? & ? & ? \\
  \bottomrule
\end{tabular}
